{ \fontfamily{ptm}\selectfont Error Bound Can Give Near Optimal Convergence Rate for Inexact Accelerated Proximal Gradient Method }

### 2025-11-14 Notebook LaTEX/EB is the key to IAGP/main.tex
>w<, changes

                \item $\omega: \RR^n \rightarrow \overline \RR$ is a closed and convex function such that it admits proximal operator $\hprox_{\lambda\omega}$ and, its conjugate $\omega^\star$ is known. 
                \item $g := \omega(Ax)$ such that $\rng A \cap \reli\dom g \neq\emptyset$. 
                \item $\omega$ is $K_\omega$ Lipschitz continuous, and $\omega^\star$ is $K_{\omega^\star}$ Lipschitz continuous and in addition, $\dom \omega^\star$ is a compact set. 

@@

                \Phi_\lambda(v_j) - \Phi_\lambda(\bar v)

@@

                    2\Vert z_j - y\Vert + \Vert \bar z - z_j\Vert 

@@

                &= \Vert z_j - \bar z\Vert\left(
                    + \frac{1}{2\lambda}\Vert \bar z - z_j\Vert
                &\underset{\text{\ref{thm:minimizing-dual-pp:item2}}}{\le} 

@@

@@

            We then solve for $\alpha_{k}$, the quadratic equation always admits one root that is strictly positive which is given as: 

@@

        This property will be crucial for analyzing the total complexity for the algorithm as a whole. 

@@

        \end{theorem}
        \begin{proof}

@@

            Terminates if $\mathbf G_\lambda(z_j, v_j) \le \epsilon$ where $\mathbf G_\lambda$ is given by \eqref{eqn:duality-gap-pp}. 

@@

                    \mathbf G_\lambda(z_j, v_j) \le

@@

@@

                \item\label{prop:inn-loop-lin-cnvg:item4} If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$. 

@@

            The smooth part of $\Phi$ is the quadratic $h(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$, it's locally Lipschitz on the compact the domain of $\dom\Psi_\lambda = \dom \omega^\star$ is compact by Assumption \ref{ass:for-inxt-prox}, hence the smooth part is Lipschitz on $\dom \omega^\star$. 

@@

                &\le \sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}\left(
                    + \frac{1}{2\lambda}\sqrt{2\lambda\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}

@@

                    + \frac{\sqrt{2\lambda}}{\lambda}\sqrt{\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}

@@

@@

                N'obliez pas à finir la demonstration d'article (iv). 

@@

        The goal of this section is to show that specific type of nonsmooth function $\omega$ that common appear in applications satisfies the error bound condition for the proximal problem, and hence the results from the previous section are applicable and relevant to practical applications. 

@@

                $\Psi$ is quasi strongly convex, with $\kappa =\lambda/\theta^2$ where $\theta$ is Hoffman constant of polyhedral set $X^+ = \argmin_{x\in \RR^n}\Psi_\lambda$, and Lipschitz smoothness constant $L_\Psi = \lambda \Vert A^\top\Vert^2$. 

@@

        The following assumption specifies conditions where the complexity of the inner using ISTA can be globally bounded for all iteration of the accelerated proximal gradient algorithm of the outer loop. 
        This is crucial for analyzing the global convergence rate of the algorithm. 

@@

            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_j^{(k)}, v_j^{(k)}\right)_{j\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional constants $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$. 

@@

                \item\label{ass:inn-cmplx:item2} There exists a constant $C_0$ such that all the initial guesses given by an algorithm in the outer loop $v_0^{(k)}$ and minimizers $\bar v^{(k)}$ satisfies $C_0 = \sup_{k \in \N \cup \{0\}}\left\Vert v_0^{(k)} - \bar v^{(k)}\right\Vert < \infty$. 
                \item\label{ass:inn-cmplx:item3} There exists the smallest error bound constant $\gamma^{\min}$ such that it lower bound all the constants for the proximal problem, i.e: $\exists \gamma_{\min}:\;0 < \gamma^{\min} \le \inf_{k \in \N \cup \{0\}} \gamma^{(k)}_\lambda$. 
                \item\label{ass:inn-cmplx:item4} $\tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}$ all satisfies error bound conditions (Assumption \ref{ass:lin-cnvg-for-pp}) with $y = \tilde y_k, \Phi_\lambda = \Phi_\lambda^{(k)}, \Psi_\lambda = \Psi_\lambda^{(k)}, L_\Phi^\lambda = L^{\lambda, (k)}_{\Phi}$ and $\gamma_\lambda = \gamma_\lambda^{(k)}$. 
                \item\label{ass:inn-cmplx:item5} The iterates of the inner loop $(z_j^{(k)}, v_j^{(k)})_{k \ge 0}$ are produced by an algorithm that satisfies Definition \ref{def:ista-inner-lp}. 
                \item\label{ass:inn-cmplx:item6}

@@

                % \item\label{prop:inner-lp-cmplx-result1} 
                % If $\lambda_1 > \lambda_2$ then $\Psi_{\lambda_1}(v) \ge \Psi_{\lambda_2}(v)$ for all $v \in \dom \omega^\star$. 
                \item\label{prop:inner-lp-cmplx-result2}  As a consequence of the former, the sequence $L_\Phi^{\lambda, (k)}$ as specified back in Fact \ref{fact:minimizing-dual-pp} is bounded above so, there exists $L_\Phi^{\max}$ such that $L_\Phi^{\max} = \sup_{k \in \N \cup \{0\}}L_\Phi^{\lambda, (k)} < \infty$. 
                \item\label{prop:inner-lp-cmplx-result3} There exists a constant $C_1$ that bounds the optimality gap of all initial guesses: 
                    \infty > C_1 \ge  \sup_{k \in \N \cup \{0\}}
                        \Psi_{\lambda}^{(k)}(v^{(k)}_0) - \Psi_\lambda^{(k)}(\bar v^{(k)})
                \item\label{prop:inner-lp-cmplx-result4} 
                There exists a constant $\infty > C_2 \ge \sqrt{C_1}\sup_{k \in \N \cup \{0\}}\left\lbrace L_\Phi^{\lambda, (k)}\sqrt{2\lambda^{(k)}} + \sqrt{C_1}\right\rbrace$. 
                \item\label{prop:inner-lp-cmplx-result5} 
                Denote $N_\epsilon$ to be the total number of iteration of inner loop needed to achieve $\mathbf G_\lambda^{(k)}(z_j, v_j) \le \epsilon$, then it's sufficient to have 
                    N_{\epsilon} = \left\lceil 
                        \frac{2\ln(\epsilon/C_2)}{
                                1 - \frac{\gamma^{\min}}{2\lambda^{\max}\left\Vert AA^\top\right\Vert}
                    \right\rceil. 

@@

            % We will start with \ref{prop:inner-lp-cmplx-result1}. 
            % After some algebra it can be shown that $\Psi_\lambda(v) = \frac{\lambda}{2}\Vert A^\top v\Vert^2 - \langle A^\top v, \tilde y_k\rangle + \omega^\star(v)$.
            % From then on it's direct, and it has $\Psi_{\lambda_1}(v) - \Psi_{\lambda_2}(v) = \frac{\lambda_1 - \lambda_2}{2}\Vert A^\top v\Vert^2 \ge 0$. 
            Before we start, note that $\Phi_\lambda^{(k)}$ is $L_{\Phi}^{\lambda, (k)}$ Lipschitz continuous from Assumption \ref{ass:lin-cnvg-for-pp} because it's assumed in item \ref{ass:inn-cmplx:item4} of Assumption \ref{ass:inn-cmplx}, and the Lipschitz constant only depends on $\lambda^{(k)}$. 
            To see \ref{prop:inner-lp-cmplx-result2},
            Recall the definition of $\Phi_\lambda^{(k)}$ from \eqref{eqn:primal-pp-k} which implies $\forall k \ge 0$, $L_{\Phi}^{\lambda, (k)}$ is the largest when $\lambda = \lambda^{\max}$. 
            We had $\lambda^{\max}$ is finite, so it has $L^{\max}_\Phi = \sup_{k \in \N \cup \{0\}}L_{\Phi}^{\lambda, (k)} < \infty$ too. 
            To see \ref{prop:inn-looplin-cnvg-item3}, we use \ref{prop:inn-looplin-cnvg-item2} and, $C_0 = \sup_{k \in \{0\}\cup \N} \left\Vert v_0^{(k)} - \bar v^{(k)} \right\Vert < \infty$ from Assumption \ref{ass:inn-cmplx}, then it's sufficient to have: $C_1 = L_{\Phi}^{\max} C_0$ by $L^{(k)}_\Phi$ Lipschitz continuity of $\Phi_\lambda^{(k)}$ as assumed in Assumption \ref{ass:lin-cnvg-for-pp}. 
            To see \ref{prop:inn-looplin-cnvg-item4}, use all previous results \ref{prop:inn-looplin-cnvg-item3}, \ref{prop:inn-looplin-cnvg-item2} and, then it's sufficient to have $C_2 = \sqrt{C_1}\left(L^{\max}_\Phi\sqrt{2\lambda^{\max}} + \sqrt{C_1}\right)$. 
            And finally, we are ready to show \ref{prop:inner-lp-cmplx-result5}, it has for all $k \ge 0$: 
                & \mathbf G_\lambda^{(k)}(z_j^{(k)}, v_j^{(k)}) 
                    1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
                    L_\Phi^{\lambda, (k)} \sqrt{2 \lambda^{(k)}} + 
                    \sqrt{\Psi_{\lambda}^{(k)}(v^{(k)}_0) - \Psi_\lambda^{(k)}(\bar v^{(k)})}
                    \Psi_{\lambda}^{(k)}(v^{(k)}_0) - \Psi_\lambda^{(k)}(\bar v^{(k)})
                    1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
                    L_\Phi^{\lambda, (k)} \sqrt{2 \lambda^{(k)}} + 
                    \sqrt{C_1}
                \right)\sqrt{C_1}
                &\underset{(3)}{\le}
                    1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
                \right)^{j/2} C_2
                &\underset{(4)}{\le}
                    1 - \frac{\gamma^{\min}}{2 \lambda^{\max}\Vert AA^\top\Vert}
                \right)^{j/2} C_2. 
            At (1), we used Theorem \ref{prop:inn-loop-lin-cnvg}. 
            At (2), we used results form \ref{prop:inner-lp-cmplx-result3} and, at (3) we used \ref{prop:inner-lp-cmplx-result4}. 
            Finally, at (4), we use the fact that the step size $\tau$ in Definition \ref{def:ista-inner-lp} which translate into our context, it has $\tau^{(k)} \ge \lambda^{(k)}\Vert AA^\top\Vert$, and hence it can be upper bounded by $\tau^{\max} := \sup_{k \in \N \cup \{0\}}\lambda^{(k)}\Vert AA^\top\Vert < \infty$. 
            Now, substitute $j = N_\epsilon$ then it's prominent that $\mathbf G_\lambda^{(k)}\left(z_j^{(k)}, v_j^{(k)}\right) \le \epsilon$ by using a logarithmic formula. 

@@

    \subsection{Overall complexity}
        We derive the overall complexity in this section. 
        Before we start, it's necessary to discuss the best initial guess vector $v^{(k)}_0$ of the inner loop so that item \ref{ass:inn-cmplx:item2} in Assumption \ref{ass:inn-cmplx} can be satisfied for as many objective functions as possible.

\appendix
    \section{Super boring chores}
        Super boring stuff that I just want to skip but somehow necessary. 
        \begin{lemma}[That conjugate for the dual of proximal problem]\;\label{lemma:chore1}\\
            Let $f:\RR^n \rightarrow \overline \RR:= \frac{1}{2\lambda}\Vert u - v\Vert^2$, then its conjugate is given by
            \begin{align*}
                f^\star(v) = \frac{1}{2\lambda}\Vert \lambda v + y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2. 
            \end{align*}
        \end{lemma}
        \begin{proof}
            Recall the following properties for any closed, proper convex function $f: \RR^n \rightarrow \overline \RR$. 
            Let $a \in \RR^n$ be any vector, let $\alpha \in \RR, c \in\RR$ be some scalar, then we have these three properties of conjugating convex funtion. 
            \begin{enumerate}[nosep]
                \item $(\alpha f)^\star = \alpha f^\star \circ (\alpha^{-1}I)$. 
                \item $(f + c)^\star(y) = f^\star(y) - c$. 
                \item $\left(x \mapsto f(x) + \langle x, y\rangle\right)^\star(y) = f^\star(y - a)$. 
            \end{enumerate}
            From here we have: 
            \begin{align*}
                f^\star(v) 
                &= 
                \left(
                   u \mapsto \lambda^{-1}\left(\frac{1}{2}\Vert u\Vert^2 - \langle u, y\rangle\right) 
                    + \frac{1}{2\lambda} \Vert y\Vert^2
                \right)^\star(v)
                \\
                &= \left(
                    u \mapsto \lambda^{-1}\left(\frac{1}{2}\Vert u\Vert^2 - \langle u, y\rangle\right) 
                \right)^\star(v)
                - \frac{1}{2\lambda} \Vert y\Vert^2
                \\
                &= 
                \left[
                    \lambda^{-1}\left(
                    u \mapsto \left(\frac{1}{2}\Vert u\Vert^2 - \langle u, y\rangle\right) 
                \right)^\star\circ(\lambda I)
                \right](v)
                - \frac{1}{2\lambda} \Vert y\Vert^2
                \\
                &= \left[
                    \lambda^{-1}\left(
                    u \mapsto \left(
                        \frac{\Vert \cdot\Vert^2}{2}
                    \right)^\star(u + y)
                \right)\circ(\lambda I)
                \right](v)
                - \frac{1}{2\lambda} \Vert y\Vert^2
                \\
                &= \left[
                    \lambda^{-1}\left(
                        u \mapsto \frac{\Vert u + y\Vert^2}{2}
                    \right)\circ(\lambda I)
                \right](v)
                - \frac{1}{2\lambda} \Vert y\Vert^2
                \\
                &= \lambda^{-1}\left(
                    \frac{1}{2}\Vert \lambda v + y\Vert^2
                \right) 
                - \frac{1}{2\lambda} \Vert y\Vert^2. 
            \end{align*}
        \end{proof}

>>>>

                \item $\omega: \RR^n \rightarrow \overline \RR$ is a closed and convex function such that it has exact proximal operator $\hprox_{\lambda\omega}$ and, with known conjugate $\omega^\star$ is known. In addition assume that $\dom \omega = \RR^n$ so that 
                \item $g: \RR^m \rightarrow \RR := \omega(Ax)$ and by previous item it satisfies constraint qualification $\rng A \cap \reli\dom \omega \neq\emptyset$. 
                \item $\omega$ is $K_\omega$ Lipschitz continuous, and $\omega^\star$ is $K_{\omega^\star}$ Lipschitz continuous and in addition, $\dom \omega^\star$ is a compact set. As an immediate consequence, the operator $\partial \omega$ is a bounded on $\RR^n$. 

@@

                \Psi_\lambda(v_j) - \Psi_\lambda(\bar v)

@@

                    \Vert z_j - \bar z\Vert + 2\Vert \bar z - y\Vert

@@

                \Vert z_j - \bar z\Vert
                    K_\omega\Vert A\Vert
                    + \lambda^{-1}\Vert \bar z - y\Vert
                    + \frac{\Vert z_j - \bar z\Vert}{2\lambda}
                \\ &\underset{\text{\ref{thm:minimizing-dual-pp:item2}}}\le 
                \sqrt{2\lambda\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
                    K_\omega\Vert A\Vert
                    + \lambda^{-1}\Vert \bar z - y\Vert
                    + \frac{\sqrt{2\lambda}}{2\lambda}\sqrt{\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)}
                &\underset{(5)}\le 
                \sqrt{2\lambda\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
                    K_\omega\Vert A\Vert
                    + \max_{z \in \partial g(\bar z)} \Vert z\Vert
                    + \frac{\sqrt{2\lambda}}{2\lambda}\sqrt{\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)}
                &\underset{(6)}= 
                \sqrt{2\lambda\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
                    K_\omega\Vert A\Vert
                    + K_\omega
                    + \frac{\sqrt{2\lambda}}{2\lambda}\sqrt{\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)}

@@

            At (5), recall the primal minimizer $\mathbf 0 \in \partial \Phi_\lambda(\bar z) = (I + \lambda\partial g)^{-1}(y)$ which means $\lambda^{-1}(y - z) \in \partial g(\bar z)$, which implies that $\lambda^{-1}\Vert y - z \Vert \le \max_{z \in \partial g}\Vert z\Vert$. 
            At (6) we used the assumption that $\omega$ is $K_\omega$ Lipschitz continuous stated in Assumption \ref{ass:for-inxt-prox}, and we invoke Lemma \ref{lemma:lipz-cnvx-fxn}. 

@@

            Then, we solve for $\alpha_{k}$, the quadratic equation always admits one root that is strictly positive which is given as: 

@@

        This property will be crucial for analyzing the total complexity for the algorithm because it is the termination criteria. 

@@

                N'obliez pas de finir cette partie.

@@

            Terminates if $\mathbf G_\lambda(z_j, v_j) \le \epsilon$ where $\mathbf G_\lambda$ is given by \eqref{eqn:duality-gap-pp}, then the result we want is $z_j$. 

@@

                    \mathbf G_\lambda(z_j, v_j) 

@@

                    C_\lambda
                    \text{ where: } 
                    C_\lambda = \sqrt{2\lambda C_\Psi^\lambda}
                        K_\omega\Vert A\Vert
                        + K_\omega

@@

                \item\label{prop:inn-loop-lin-cnvg:item4} If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$ and the number of iterations sufficient to achieve the accuracy would be 
                    j \ge 
                    \left\lceil\frac{
                        2\ln \left(
                            \frac{\epsilon}{C_\lambda}
                    }{
                    }\right\rceil. 

@@

            The smooth part of $\Phi_\lambda$ is the quadratic $h(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$, it's locally Lipschitz on the compact the domain of $\dom\Psi_\lambda = \dom \omega^\star$ is compact by Assumption \ref{ass:for-inxt-prox}, hence the smooth part is Lipschitz on $\dom \omega^\star$. 

@@

                \sqrt{2\lambda\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
                    K_\omega\Vert A\Vert
                    + K_\omega
                    + \frac{\sqrt{2\lambda}}{2\lambda}\sqrt{\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)}

@@

                    K_\omega\Vert A\Vert
                    + K_\omega
                    + \frac{\sqrt{2\lambda}}{\lambda}\sqrt{\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)}

@@

                    K_\omega\Vert A\Vert
                    + K_\omega

@@

            To see \ref{prop:inn-loop-lin-cnvg:item4}, use Theorem \ref{thm:dlty-gap-inxt-pp} and the rest is just some algebra because $\gamma/(2\tau) \le 1$ from \ref{thm:lin-cnvg-ista-eb}. 

@@

        Continuing our discussion from the previous section, the goal of this section is to show that there exists specific type of $\omega$ that appears in applications and satisfies the error bound condition for the proximal problem $\Phi_\lambda$, and hence the results from the previous section are applicable and relevant to practical applications. 

@@

                $\Psi$ is quasi strongly convex, with $\kappa =\lambda/\theta^2$ where $\theta$ is a Hoffman constant of polyhedral set $X^+ = \argmin_{x\in \RR^n}\Psi_\lambda$, and Lipschitz smoothness constant $L_\Psi = \lambda \Vert A^\top\Vert^2$. 

@@

        The following assumption specifies conditions where the complexity of the inner using ISTA can be globally bounded for all iteration of the accelerated proximal gradient algorithm of the outer loop independent of the initial guess $v_0^{(k)}$, $\lambda^{(k)}$. 

@@

            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_j^{(k)}, v_j^{(k)}\right)_{j\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional constants $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}$. 

@@

                \item\label{ass:inn-cmplx:item2} There exists the smallest error bound constant $\gamma^{\min}$ such that it lower bound all the constants for the proximal problem, i.e: $\exists \gamma_{\min}:\;0 < \gamma^{\min} \le \inf_{k \in \N \cup \{0\}} \gamma^{(k)}_\lambda$. 
                \item\label{ass:inn-cmplx:item3} $\tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}$ all satisfies error bound conditions (Assumption \ref{ass:lin-cnvg-for-pp}) with $y = \tilde y_k, \Phi_\lambda = \Phi_\lambda^{(k)}, \Psi_\lambda = \Psi_\lambda^{(k)}, L_\Phi^\lambda = L^{\lambda, (k)}_{\Phi}$ and $\gamma_\lambda = \gamma_\lambda^{(k)}$. 
                \item\label{ass:inn-cmplx:item4} The iterates of the inner loop $\left(z_j^{(k)}, v_j^{(k)}\right)_{k \ge 0}$ are produced by an ISTA algorithm satisfying Definition \ref{def:ista-inner-lp}. We choose the same stepsize $\tau = 1/\Vert A^T A\Vert$ for all iteration of ISTA. 

@@

            Then, the total number of inner loop iteration sufficient to achieve $\mathbf G_\lambda^{(k)}\left(z_j^{(k)}, v_j^{(k)}\right) \le \epsilon_k$, at each iteration $k$ denoted by $J^{(k)}_\epsilon$ can be upper bounded by:

        \end{proposition}
        \begin{proof}
            To prove the above theorem, we use the results from Proposition \ref{prop:inn-loop-lin-cnvg} into the context of the iterations in the outer loop.

        \end{proof}
    \subsection{Overall complexity}
        We derive the overall complexity in this section. 
        Before we start, it's necessary to discuss the best initial guess vector $v^{(k)}_0$ of the inner loop so that item \ref{ass:inn-cmplx:item2} in Assumption \ref{ass:inn-cmplx} can be satisfied for as many objective functions as possible.

\appendix
    \section{Super boring chores}
        Super boring stuff that I just want to skip but somehow necessary. 
        \begin{lemma}[That conjugate for the dual of proximal problem]\;\label{lemma:chore1}\\
            Let $f:\RR^n \rightarrow \overline \RR:= \frac{1}{2\lambda}\Vert u - v\Vert^2$, then its conjugate is given by
                f^\star(v) = \frac{1}{2\lambda}\Vert \lambda v + y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2. 

@@

            Recall the following properties for any closed, proper convex function $f: \RR^n \rightarrow \overline \RR$. 
            Let $a \in \RR^n$ be any vector, let $\alpha \in \RR, c \in\RR$ be some scalar, then we have these three properties of conjugating convex funtion. 
                \item $(\alpha f)^\star = \alpha f^\star \circ (\alpha^{-1}I)$. 
                \item $(f + c)^\star(y) = f^\star(y) - c$. 
                \item $\left(x \mapsto f(x) + \langle x, y\rangle\right)^\star(y) = f^\star(y - a)$. 
            From here we have: 
                f^\star(v) 
                   u \mapsto \lambda^{-1}\left(\frac{1}{2}\Vert u\Vert^2 - \langle u, y\rangle\right) 
                    + \frac{1}{2\lambda} \Vert y\Vert^2
                \right)^\star(v)
                    u \mapsto \lambda^{-1}\left(\frac{1}{2}\Vert u\Vert^2 - \langle u, y\rangle\right) 
                \right)^\star(v)
                - \frac{1}{2\lambda} \Vert y\Vert^2
                \left[
                    \lambda^{-1}\left(
                    u \mapsto \left(\frac{1}{2}\Vert u\Vert^2 - \langle u, y\rangle\right) 
                \right)^\star\circ(\lambda I)
                \right](v)
                - \frac{1}{2\lambda} \Vert y\Vert^2
                &= \left[
                    \lambda^{-1}\left(
                    u \mapsto \left(
                        \frac{\Vert \cdot\Vert^2}{2}
                    \right)^\star(u + y)
                \right)\circ(\lambda I)
                \right](v)
                - \frac{1}{2\lambda} \Vert y\Vert^2
                &= \left[
                    \lambda^{-1}\left(
                        u \mapsto \frac{\Vert u + y\Vert^2}{2}
                    \right)\circ(\lambda I)
                \right](v)
                - \frac{1}{2\lambda} \Vert y\Vert^2
                &= \lambda^{-1}\left(
                    \frac{1}{2}\Vert \lambda v + y\Vert^2
                - \frac{1}{2\lambda} \Vert y\Vert^2. 

@@

        \begin{lemma}[Lipschitz constant of convex function]\;\label{lemma:lipz-cnvx-fxn}
            Let $f: \RR^n \rightarrow \overline \RR$ be a closed, convex, proper function. 
            Let $\partial f$ be its convex subgradient. 
            Then, 
                \item for all $x\in \RR^n, y\in \RR^n$ it has: $|f(x) - f(y)| \le \sup_{x\in \dom \partial f}\ (\partial f(x) \;|\; \mathbf 0)\Vert y - x\Vert$. 
                \item If in addition, the function is $K_f$ Lipschitz continuous globally on $\RR^n$, then: $(\forall y \in \RR^n)(\forall v_y \in \partial f(y)):\; K_f \ge \Vert v_y\Vert$. 
            The proof is direct. 
            Let $x, y \in \RR^n$ be arbitrary.
            Choose $v_x \in \partial f(y)$ and $v_y \in \partial f(y)$ such that $\Vert v_x\Vert = \dist (\partial f(x) | \mathbf 0), \Vert v_y\Vert = \dist (\partial f(y) | y)$ which is possible because $\partial f(x)$ is closed for all $x \in \dom \partial f$. 
            Therefore, we have the following. 
                |f(x) - f(y) | &\le 
                \max(f(x) - f(y), f(y) - f(x))
                &\underset{(1)}\le \max(-\langle v_x, y - x\rangle, - \langle v_y, x - y\rangle)
                &\le \max(\Vert v_x\Vert, \Vert v_y\Vert)\Vert y - x\Vert
                &\le \left(
                    \sup_{x \in \dom \partial f} \dist(\partial f(x) \;|\; \mathbf 0)
                \right)\Vert y - x\Vert. 
            At (1), we used the fact that $f(x) - f(y) \le - \langle v_x, y - x\rangle$ and, $f(y) - f(x) \le - \langle v_y, x - y\rangle$ by convex subgradient inequality. 
            For the second results it's direct, choose any $y \in \dom f = \RR^n, v_y \in \partial f(y)$, then there exists some $x \in \RR^n$: 
                0&\le \frac{f(x) - f(y)}{\Vert x - y\Vert} 
                - \frac{\langle v_y, x - y\rangle}{\Vert x - y\Vert}
                K_f - \left\langle 
                    v_y, \frac{x - y}{\Vert x - y\Vert}
                \right\rangle
                &= K_f - \Vert v_y\Vert. 
            AT (1), consider chosing any $x$ such that $\frac{x - y}{\Vert x - y\Vert} = \frac{v_y}{\Vert v_y\Vert}$, this is possible because the domain of $f$ is $\RR^n$. 
